Quantifying the home ground advantage with `hyper2` and `hyper3` objects

### 2025-02-13 inst/home_advantage.Rmd
Rangers and Celtic

```{r scottychisq,cache=TRUE}
o
scot_max_lambda <- o$maximum
maxL <- f(scot_max_lambda)

@@

```{r scotmax}
(H <- home_away3(home_away_table(a,give=FALSE),scot_max_lambda))  # o$maximum ~= 1.353
maxp(H,give=1)
```

@@

```{r sfasdf, cache=TRUE}
o$maximum
mH3 <- maxp(home_away3(home_away_table(a,give=FALSE),scot_max_lambda),give=FALSE)
round(mH3*1000)
```

@@

```{r}
mH
mH["Rangers"]
mH["home"]
mH3
lambda <- scot_max_lambda
h2_exp <- matrix(0,4,4)
rownames(h2_exp) <- teams
colnames(h2_exp) <- teams
h3_exp <- h2_exp
n_matches <- Re(aF) + Im(aF)
for(hometeam in teams){
    for(awayteam in teams){

@@

        h3_exp[hometeam,awayteam] <- (
            n_matches[hometeam,awayteam] * (lambda* mH3[hometeam])/
            (lambda* mH3[hometeam] + mH3[awayteam])
        )

        h3_exp[hometeam,awayteam] %<>%
            add(1i*
                n_matches[hometeam,awayteam] * (mH3[awayteam])/
                (lambda* mH3[hometeam] + mH3[awayteam])
        )
    }
}
aF
round(h2_exp,1)
round(h3_exp,1)

@@

            h3_exp[hometeam,awayteam] <- (
                n_matches[hometeam,awayteam] * (lambda* mH3[hometeam])/
                (lambda* mH3[hometeam] + mH3[awayteam])
            )

            h3_exp[hometeam,awayteam] %<>%
                add(1i*
                    n_matches[hometeam,awayteam] * (mH3[awayteam])/
                    (lambda* mH3[hometeam] + mH3[awayteam])
                    )
        }
    }
    return(h3_exp)
}

round(expectation3(mH3[c("Rangers","Celtic","Falkirk","Livingston")],aF,scot_max_lambda),1)
```

@@

Following lines create `baseball.rda`, residing in the `data/`
directory of the package.

```{r,label=savesolingdataset}
save(baseball_table, baseball, baseball_maxp, 
  file="baseball.rda")
```

>>>>

```{r scottychisq,cache=TRUE}
o
RCLF3_lambda_max <- o$maximum
maxL <- f(RCLF3_lambda_max)

@@

```{r scotmax}
(H <- home_away3(home_away_table(a,give=FALSE),RCLF3_lambda_max))  # o$maximum ~= 1.353
maxp(H,give=1)
```

@@

```{r sfasdf, cache=TRUE}
RCLF3_lambda_max <- o$maximum
RCLF3_max <- maxp(home_away3(home_away_table(a,give=FALSE),RCLF3_lambda_max),give=FALSE)
round(RCLF3_max * 1000)
```

@@

```{r}
mH
mH["Rangers"]
mH["home"]
RCLF3_max
lambda <- RCLF3_lambda_max
h2_exp <- matrix(0,4,4)
rownames(h2_exp) <- teams
colnames(h2_exp) <- teams
h3_exp <- h2_exp
n_matches <- Re(aF) + Im(aF)
for(hometeam in teams){
    for(awayteam in teams){

@@

        h3_exp[hometeam,awayteam] <- (
            n_matches[hometeam,awayteam] * (lambda* RCLF3_max[hometeam])/
            (lambda* RCLF3_max[hometeam] + RCLF3_max[awayteam])
        )

        h3_exp[hometeam,awayteam] %<>%
            add(1i*
                n_matches[hometeam,awayteam] * (RCLF3_max[awayteam])/
                (lambda* RCLF3_max[hometeam] + RCLF3_max[awayteam])
        )
    }
}
aF
round(h2_exp,1)
round(h3_exp,1)

@@

            h3_exp[hometeam,awayteam] <- (
                n_matches[hometeam,awayteam] * (lambda* RCLF3_max[hometeam])/
                (lambda* RCLF3_max[hometeam] + RCLF3_max[awayteam])
            )

            h3_exp[hometeam,awayteam] %<>%
                add(1i*
                    n_matches[hometeam,awayteam] * (RCLF3_max[awayteam])/
                    (lambda* RCLF3_max[hometeam] + RCLF3_max[awayteam])
                    )
        }
    }
    return(h3_exp)
}

round(expectation3(RCLF3_max[c("Rangers","Celtic","Falkirk","Livingston")],aF,RCLF3_lambda_max),1)
```

@@

Following lines create `RCLF.rda`, residing in the `data/`
directory of the package.

```{r,label=savesolingdataset}
RCLF3_table <- home_away_table(a, give=TRUE, teams = teams)

save(RCLF3_table,  RCLF3_max, RCLF3_lambda_max, file="RCLF.rda")
```
